\subsection{Subsystem Engineering Design}
\textit{- Refer to Kossiakoff, Chapter 13, 15 and 16\\
-	In Section 2.8, attach a one-page excerpt from your handwritten lab book as an example for each heading in this section (eight pages in total)}

\subsubsection{Constraints and trade-offs}

\subsubsubsection{Design Constraints}
\textit{-	Where were you constrained in implementation of the concept?}

% Write about design constraints here

\subsubsubsection{Trade-offs}
\textit{-	Which trade-offs did you consider? How did you make your eventual selections, and why?}

% Write about trade-offs here

\subsubsection{Tools and Methods}

\subsubsubsection{Engineering tools}
\textit{-	Discuss the engineering tools that you used (hardware tools, simulation packages, etc) and motivate their use. This does NOT mean physical hand tools like soldering irons, pliers, etc!}

% Write about engineering tools here

\subsubsubsection{Engineering methods}
\textit{-	Discuss the engineering methods that you used (design methods, prototyping approach, simulation, test benches, etc) and motivate their use. Did you apply agile, waterfall, V-shaped development? If you used parameter sweeps and CAD-based design methods, describe them here. }

% Write about engineering methods here

\subsubsection{Selected design details}
\textit{-	Provide selected details of your design, including circuit schematics, simulation results. Start out by listing which design elements (circuits, code snippets) you will present.}

\subsubsubsection{Statements of requirements}
\textit{Briefly state the high-level requirements of your individually designed circuits and / or code segments.}

% Write your requirements here

\subsubsubsection{Development}
\textit{-	Demonstrate top-down definition with bottom-up implementation (or some other approach commensurate with your selected design approach) of your selected detail designs, motivated by flow charts, design equations, or some other guiding input. }

% Write about development here

\subsubsubsection{Simulations}
\textit{-	Where appropriate, demonstrate circuit simulations, test bench operation, or some other form of computer verification of operation prior to deployment.}

% Add simulations here

\subsubsubsection{Approach to coding and testing}
\textit{-	Describe your approach to microcontroller coding and code testing, with selected examples.}

% Write about coding and testing here
